---
title: "Weight of Fish"
author: "Jaelynn Schultz"
date: "Summer 2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
fishdata<-read.csv(file = "Fish.csv")
```

# Predicting Fish Weight


## Perch

```{r}
FishPerch<-filter(fishdata, Species == "Perch")
FishPerch<-select(FishPerch, -Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishPerch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model

The best two regressor model is the one showing Height and Weight variables as the two regressors. The next best regressor model would be the one featuring Length 3, Height, and Weight as the regressor variables. 

## Pike

```{r}
FishPike<-filter(fishdata, Species == "Pike")
FishPike<-select(FishPike, -Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishPike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model

The best regressor model is the one that features Length 1, Length 2, Length 3, Height, and Width variables as its two regressors. The following best is the model showing length 1, length 3, height, and weight as its regressor variables. 

## Roach

```{r}
FishRoach<-filter(fishdata, Species == "Roach")
FishRoach<-select(FishRoach, -Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishRoach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model

The best regressor model is the one featuring Length 3 and Weight as its two regressors. The following best is the model showing just weight as its regressor variable. 

## Final Summary Statements

As for the weight prediction of each fish species including roach, pike, and perch, we can see that the Adjusted R-Values do differ, but are still similar in value in the best regression models. Again, in terms of the weight prediction of each species, the Adjusted R-squared value for Perch on the best regression model is 0.9400. The Adjusted R-squared value for Pike on the best regression model is 0.980. Finally, the Adjusted R-squared value for Roach on the best regression model is 0.850. 
